---
title: "JulyN Summary"
author: "RLionheart"
date: "07/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This Control.Rmd script outlines the order in which the MESOSCOPE B12 Incubation code snippets are to be run. 

As with most targeted analyses, the first step is to run the raw csv data through our Import -> Quality Control -> BMIS, and if applicable, -> Quantify.

The below chunk imports the raw MSDIAL files and combines them to one file in long format for analysis, then applies Quality Control and BMIS.
Output can be found in data_processed/ containing the keyword MSDial_combined.
```{r Import Files, include=TRUE}
source("src/Import_files.R")
source("src/Quality_Control.R")
source("src/B12_BMIS_HILIC.R")
```

Next step is to 
Process osmolytes
Split.by.eddy
chl uploads standardize
NMDS

should be in any order:
ANOSIM_species indic (STILL NEEDS LOTS OF WORK)
ANOVA_all (mostly useless. needs work.)
anova b12
anova dsw
univariate stats
heatmaps

### Chl-A Normalizations
#### Heatmaps





While it looks like the Cyclonic Control is more abundant in the Chl-A normalized data, that pattern doesn't seem to carry over to the Anticyclonic data. Instead, the B12-enriched sample seems to be the most abundant when normalized to Chl-A in the Anticyclonic set.

#### NMDS 

First, looking at the Cyclonic eddy NMDS figures with and without chlorophyll normalization. Remember that position is arbitrary, only distances are relevant.

And the Anticyclonic eddies:


There are some challenges in absorbing these graphs, one of which is that we don't have every data point. So some of the triangles are incomplete. But what I'm taking away from it is that deep seawater and no B12 have the most distinct positions, regardless of Chl normalizations.

### Osmolytes

For now I am starting with the Chl-normalized osmolyte heatmaps. I think this is a good place to start, but I can also compare the Chl-normalized to the non-normalized images too. Below are the NMDS images for osmolytes.

And the Anticyclonic:

I'm seeing the same pattern echoed from the large heatmaps (to be expected since it's the same data with fewer points) but maybe it would be helpful to see the differences between osmolytes and non-osmolytes; are osmolytes affected/driving the process more?

#### Osmolytes NMDS images

Cyclonic eddy, normalized to Chl and filtered for Osmolytes


Anticyclonic eddy, normalized to Chl and filtered for Osmolytes


That anticyclonic image is really interesting; it looks like most of the osmolytes are closely related distance-wise in the anticyclonic eddy.


### Glutamate:Glutamine ratios
Normalized to RF and plot those ratios and percentages.


### What I'd like to do next (and timeline)

I think it will be valuable to try and do a kmeans clustering on the entire thing, as well as a complete NMDS on all eddies and filter sizes. My goal is to see if there's interesting patterns between eddies and sizes, maybe it will be easier to see treatment differences. 

Since we only have peak areas and these were run at different times, I'm not sure it's possible (usually it's not good to compare between runs?). I can start with those that are normalized to Chl.

If I have time, I'd also like to see if Osmolytes are significantly more different between treatments than non-Osmolytes.
