---
title: "Fold Change with Abundance plot"
author: "Katherine Heal"
date: "November 6, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
library("vegan")
library("pastecs")
library("simba")
library("ecodist")
library("MASS")
library("caret")
library("e1071")
library("cowplot")
library(tidyverse)
#library(dplyr)
#library(plyr) 
#library(ggplot2) 
library(gridExtra) 
library(seqinr) 
library(lubridate)
#library(reshape2)
library(tidyr)
library(Hmisc)
library(gtools)
library(cowplot)
require(RColorBrewer)
library(readr)
library(plotly)
library(stringr)
library(devtools)
library(RCurl)


source('~/Google_Drive/6_Classes/1_FISH560/R_SourceCode/coldiss.R', encoding = 'UTF-8' )
source('~/Google_Drive/6_Classes/1_FISH560/R_SourceCode/biostats.R', encoding = 'UTF-8' )
setwd("~/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/F5_NMDSplots")

Experiment1 <- "Reanalysis_1335_B12Light_Exp_Rerun"
Experiment2 <- "Reanalysis_NP_B12Light_Exp"
Location <- "~/Google_Drive/00_XCMS_Working/"
ExpDIR1 <-paste(Location, Experiment1, sep = "", collapse = NULL)
ExpDIR2 <-paste(Location, Experiment2, sep = "", collapse = NULL)
```


#Get wide data with stats
```{r, warning=FALSE, message=FALSE}
setwd("~/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/1_Targeted_DataAnalysis/TP")
TPTQSdatAll <- read_csv("Combined/Filtered_Wide_Combined_wStats.csv",comment = "#")
TPTQSdat <- TPTQSdatAll %>% select(LB12HL_AB:RB12LL_EF) %>% as.data.frame()
row.names(TPTQSdat) <- TPTQSdatAll$Compound.Name
TPTQSdat <- t(TPTQSdat)
TPTreatDat <- read.csv('Treatment_data.csv',header=TRUE, row.names=1)


TPQEdatAll <- read_csv(paste(ExpDIR1, "/Combined/Filtered_wide_Combined_BioNormedFilteredBMISd_wStats_wMS2_wIDs.csv", sep = "")) %>%
  arrange(desc(LB12_ave)) %>%
  head(500)
TPQEdat <- TPQEdatAll %>%  select(LB12HL_AB:RB12LL_EF) %>% as.data.frame()
row.names(TPQEdat) <- TPQEdatAll$MF_Frac
#Try <- TPQEdat %>% mutate(Sums = rowMeans(TPQEdat)) %>% filter(is.na(Sums))
TPQEdat <- t(TPQEdat)

setwd("~/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/1_Targeted_DataAnalysis/NP")
NPTQSdatAll <- read_csv("Combined/Filtered_Wide_Combined_wStats.csv",comment = "#")
NPTQSdat <- NPTQSdatAll %>% select(LB12HL_AB:RB12LL_EF) %>% as.data.frame()
row.names(NPTQSdat) <- NPTQSdatAll$Compound.Name
NPTQSdat <- t(NPTQSdat)

NPQEdatAll <- read_csv(paste(ExpDIR2, "/Combined/Filtered_wide_Combined_BioNormedFilteredBMISd_wStats_wMS2_wIDs.csv", sep = ""))%>%
  arrange(desc(LB12_ave)) %>%
  head(500)
NPQEdat <- NPQEdatAll %>%  select(LB12HL_AB:RB12HL_EF) %>% as.data.frame()
row.names(NPQEdat) <- NPQEdatAll$MF_Frac
NPQEdat <- t(NPQEdat)

```

#Standarize the data
```{r Standaradize, warning=FALSE, message=FALSE}
TPExpDat.std <- data.stand(TPTQSdat,method='standardize',margin='column',plot=F)
NPExpDat.std <- data.stand(NPTQSdat,method='standardize',margin='column',plot=F)
TPExpDatQE.std <- data.stand(TPQEdat,method='standardize',margin='column',plot=F)
NPExpDatQE.std <- data.stand(NPQEdat,method='standardize',margin='column',plot=F)
```

#Make TQS plots, do TQS stats
##NMDS with all compounds for TP with TQS data, 
perform the NMDS, make plot, write out csv of vectors with p < 0.01, perfom anosim
```{r NMDS, warning=FALSE, message=FALSE, results = FALSE}
tp.nmds<-metaMDS(TPExpDat.std, distance='euclidean', k=2, autotransform=FALSE, wascores = FALSE, noshare = FALSE, trymax=10000)
#vec.tp<-envfit(tp.nmds$points, TPExpDat.std, perm=1000)
pointlocation <- tp.nmds[['points']] %>% as.data.frame() %>% cbind(TPTreatDat)

g<- ggplot(data = pointlocation, aes(x =MDS1, y =  MDS2, fill = Light.Status, 
                                     shape = Cobalamin.Status, group = Supergroup))+
  geom_polygon(fill = NA, color = "black") +
  geom_point(size = 3) + 
  scale_shape_manual(values = c(22,21)) +
  scale_fill_manual(values = c("grey","black")) +   
  ggtitle("Thalassiosira pseudonana") +
  theme(plot.title = element_text(face= "italic", size = 9),
        axis.title.x = element_blank(),
        axis.title.y = element_text( size = 8),
        axis.text = element_text(size = 8))+
  labs(y="Axis 2") +
  theme(legend.position="none")
g


#Get and write out vector info, write out CSV into the correct folder.-----
vec.info<-envfit(tp.nmds$points, TPExpDat.std, perm=9999)
names <- as.data.frame(vec.info[[1]][[1]])%>%
  mutate(Compound.Name = row.names(.),
         pvalues = vec.info[[1]][[4]]) %>%
  select(Compound.Name, pvalues)

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T12_NMDSVectors")
#write_csv(names, "TP_TQS_vectors.csv")

#Get and write out ANOSIM data info
TPLight.anosim<-anosim(TPExpDat.std,TPTreatDat[,4], distance = 'euclidean')
TPLightanosimResults <- c("Tp", "Light", TPLight.anosim$statistic, TPLight.anosim$signif)
TPB12.anosim<-anosim(TPExpDat.std,TPTreatDat[,3], distance = 'euclidean')
TPB12anosimResults <- c("Tp", "Cobalamin", TPB12.anosim$statistic, TPB12.anosim$signif)
AnosimResults <- data.frame(x = TPLightanosimResults,  y = TPB12anosimResults, z= c("Org", "Variable", "ANOSIMStat", "ANOSIMpvalue"))

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T11_NMDSANOSIM_stats")
#write_csv(AnosimResults, "TP_TQS_anosimstats.csv")

```

##NMDS with all compounds for NP with TQS data
```{r NMDS, warning=FALSE, message=FALSE}
np.nmds<-metaMDS(NPExpDat.std, distance='euclidean', k=2, autotransform=FALSE, wascores = FALSE, noshare = FALSE, trymax=1000)
pointlocation <- np.nmds[['points']] %>% as.data.frame() %>% cbind(TPTreatDat)

#ordiplot(np.nmds, type="text", display="sites", xlab="Axis 1", ylab="Axis 2")
#plot(vec.info, p.max=.001, col="blue")



h<- ggplot(data = pointlocation, aes(x =MDS1, y =  MDS2, fill = Light.Status, 
                                     shape = Cobalamin.Status, group = Supergroup))+
  geom_polygon(fill = NA, color = "black") +
  geom_point(size = 3) + 
  scale_shape_manual(values = c(22,21)) +
  scale_fill_manual(values = c("grey","black")) +   
  ggtitle("Navicula pelliculosa") +
  theme(plot.title = element_text(face= "italic", size = 9),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text = element_text(size = 8))+
  theme(legend.position="none")

h

#Get and write out vector info, write out CSV into the correct folder.-----
vec.info<-envfit(np.nmds$points, NPExpDat.std, perm=9999)
names <- as.data.frame(vec.info[[1]][[1]])%>%
  mutate(Compound.Name = row.names(.),
         pvalues = vec.info[[1]][[4]]) %>%
  select(Compound.Name, pvalues)

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T12_NMDSVectors")
#write_csv(names, "NP_TQS_vectors.csv")

#Get and write out ANOSIM data info
NPLight.anosim<-anosim(NPExpDat.std,TPTreatDat[,4], distance = 'euclidean')
NPLightanosimResults <- c("Np", "Light", NPLight.anosim$statistic, NPLight.anosim$signif)
NPB12.anosim<-anosim(NPExpDat.std,TPTreatDat[,3], distance = 'euclidean')
NPB12anosimResults <- c("Np", "Cobalamin", NPB12.anosim$statistic, NPB12.anosim$signif)
AnosimResults <- data.frame(x = NPLightanosimResults,  y = NPB12anosimResults, z= c("Org", "Variable", "ANOSIMStat", "ANOSIMpvalue"))

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T11_NMDSANOSIM_stats")
#write_csv(AnosimResults, "NP_TQS_anosimstats.csv")

```


#Make QE plots, do QE stats
##NMDS with all compounds for TP with QE data
```{r NMDS, warning=FALSE, message=FALSE}
TPExpDatQE.std <- TPExpDatQE.std[, !colSums(!is.finite(as.matrix(TPExpDatQE.std)))]
tp.nmds<-metaMDS(TPExpDatQE.std, distance='euclidean', k=2, autotransform=FALSE, wascores = FALSE, noshare = FALSE, trymax=10000)
#vec.tp<-envfit(tp.nmds$points, TPExpDat.std, perm=1000)
pointlocation <- tp.nmds[['points']] %>% as.data.frame() %>% cbind(TPTreatDat)

a<- ggplot(data = pointlocation, aes(x =MDS1, y =  MDS2, fill = Light.Status, 
                                     shape = Cobalamin.Status, group = Supergroup, label = row.names(pointlocation)))+
  geom_polygon(fill = NA, color = "black") +
  #geom_text()+
  geom_point(size = 3) + 
  scale_shape_manual(values = c(22,21)) +
  scale_fill_manual(values = c("grey","black")) +   
  theme(plot.title = element_text(face= "italic"))+
  labs(x="Axis 1",y="Axis 2") +
  theme(legend.position="none",
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 8))


 #Get and write out vector info, write out CSV into the correct folder.-----
vec.info<-envfit(tp.nmds$points, TPExpDatQE.std, perm=999)
names <- as.data.frame(vec.info[[1]][[1]])%>%
  mutate(Compound.Name = row.names(.),
         pvalues = vec.info[[1]][[4]]) %>%
  select(Compound.Name, pvalues)

a

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T12_NMDSVectors")
#write_csv(names, "TP_QE_vectors.csv")

#Get and write out ANOSIM data info
TPLight.anosim<-anosim(TPExpDatQE.std,TPTreatDat[,4], distance = 'euclidean')
TPLightanosimResults <- c("Tp", "Light", TPLight.anosim$statistic, TPLight.anosim$signif)
TPB12.anosim<-anosim(TPExpDatQE.std,TPTreatDat[,3], distance = 'euclidean')
TPB12anosimResults <- c("Tp", "Cobalamin", TPB12.anosim$statistic, TPB12.anosim$signif)
AnosimResults <- data.frame(x = TPLightanosimResults,  y = TPB12anosimResults, z= c("Org", "Variable", "ANOSIMStat", "ANOSIMpvalue"))

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T11_NMDSANOSIM_stats")
#write_csv(AnosimResults, "TP_QE_anosimstats.csv")
```

##NMDS with all compounds for NP with QE data
```{r NMDS, warning=FALSE, message=FALSE}
NPExpDatQE.std <- NPExpDatQE.std[, !colSums(!is.finite(as.matrix(NPExpDatQE.std)))]
np.nmds<-metaMDS(NPExpDatQE.std, distance='euclidean', k=2, autotransform=FALSE, wascores = FALSE, noshare = FALSE, trymax=10000)
#vec.tp<-envfit(tp.nmds$points, TPExpDat.std, perm=1000)
pointlocation <- np.nmds[['points']] %>% cbind(TPTreatDat)

b<- ggplot(data = pointlocation, aes(x =MDS1, y =  MDS2, fill = Light.Status, 
                                     shape = Cobalamin.Status, group = Supergroup, label = Supergroup))+
  geom_polygon(fill = NA, color = "black") +
  geom_point(size = 3) + 
  scale_shape_manual(values = c(22,21)) +
  scale_fill_manual(values = c("grey","black")) +   
  theme(plot.title = element_text(face= "italic"),
        axis.title.y = element_blank())+
  labs(x="Axis 1") +
  theme(legend.position="none",
        axis.text = element_text(size = 8),
        axis.title.x = element_text(size =8))
b
#ordiplot(np.nmds, type="text", display="sites", xlab="Axis 1", ylab="Axis 2")
#plot(vec.info, p.max=.001, col="blue")


#Get and write out vector info, write out CSV into the correct folder.-----
vec.info<-envfit(np.nmds$points, NPExpDatQE.std, perm=999)
names <- as.data.frame(vec.info[[1]][[1]])%>%
  mutate(Compound.Name = row.names(.),
         pvalues = vec.info[[1]][[4]]) %>%
  select(Compound.Name, pvalues)

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T12_NMDSVectors")
#write_csv(names, "NP_QE_vectors.csv")

#Get and write out ANOSIM data info
NPLight.anosim<-anosim(NPExpDatQE.std,TPTreatDat[,4], distance = 'euclidean')
NPLightanosimResults <- c("Np", "Light", NPLight.anosim$statistic, NPLight.anosim$signif)
NPB12.anosim<-anosim(NPExpDatQE.std,TPTreatDat[,3], distance = 'euclidean')
NPB12anosimResults <- c("Np", "Cobalamin", NPB12.anosim$statistic, NPB12.anosim$signif)
AnosimResults <- data.frame(x = NPLightanosimResults,  y = NPB12anosimResults, z= c("Org", "Variable", "ANOSIMStat", "ANOSIMpvalue"))

setwd("/Users/katherineheal/Google_Drive/0_Manuscripts/_Heal_DiatomsCobalamin/_Working_manuscript/2_Figures_Working/T11_NMDSANOSIM_stats")
#write_csv(AnosimResults, "NP_QE_anosimstats.csv")



```





##Combine NP and TP TQS plots
```{r Combined TQS NMDS, warning=FALSE, message=FALSE}
j <- plot_grid(g, h, a, b, labels = "AUTO", ncol = 2,   align = 'v')
j
#ggsave(j, filename = "/Users/katherineheal/Google_Drive/0_Manuscripts/_B12_Demand_Cultures_paper/_Working_manuscript/2_Figures_Working/F5_NMDSplots/QEandTQS_NMDS.pdf", width = 5.5, height = 5.2, units = "in", device = pdf)
```




